DataCamp: An Interactive Teaching Tool

### 2018-01-03 manuscript.tex
add title
added to manuscript

%-----------------------------------------------------------------------------------------------------
%Substitute this all with tise_style
\documentclass[12pt]{article}
\usepackage{natbib}  % used for citations
\usepackage[parfill]{parskip} %used for formatting style of text
\usepackage{url}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{fancyvrb}
% Sets margins to 1 in
%\addtolength{\oddsidemargin}{-.5in}%
%\addtolength{\evensidemargin}{-.5in}%
%\addtolength{\textwidth}{1in}%
%\addtolength{\textheight}{1.3in}%
%\addtolength{\topmargin}{-.8in}%
%-----------------------------------------------------------------------------------------------------

\title{Enter our title here}

\author{Tessa Mcdonnel, Shannon Pileggi,  \\Statistics Department, California Polytechnic State University, San Luis Obispo}
%\author{Shannon Pileggi \\Statistics Department, California Polytechnic State University, San Luis Obispo}

\begin{document}

@@

Questions:

How do I say that LaTeX is compatible with datacamp?

I can't find the swirl package on mendeley so im not sure how to add that.

How did the linking with LMS process go?

It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to
unfold, the use of statistical software has become increasingly emphasized in education \citep{AmericanStatisticalAssociation2016}. By integrating the
capabilities of technology in statistics courses, students can explore fundamental concepts by analyzing and
interpreting real data sets \citep{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is practiced outside of the
classroom \citep{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
(GAISE) College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators
to use technology "as a way to explore conceptual ideas and enhance student learning" \citep{AmericanStatisticalAssociation2016}.

The goal for any statistics course is to help students develop the ability to think statistically
\citep{AmericanStatisticalAssociation2016}.
Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as
variability, randomness and hypothesis testing. Although numerous statistical technologies exist, R and R Studio
provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses \citep{Chance2007}. R
allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark
an interest in the domain of statistics \citep{Wang2017}.

With this increased use of R in classrooms, there is a need for an effective way to get students familiar with statistical software
\citep{Baumer2014}. While R software provides users with extraordinary capabilities, there is no doubt a steep learning curve. To facilitate
this transition to R programming, popular interactive teaching technologies have been created including swirl (** need to cite package**), LearnR and TryR. 
These tools allow students to work through coding problems while recieving immediate feedback in and out of the classroom. swirl is an
open source R package that allows students to learn R programing in their R console. This interactive learning tool
contains several pre-existing lessons but what makes swirl so popular is its versitality; educators can also create their own
lesson to fit the curriculum and assign it to students \citep{Carchedi2014}.
While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, integration of learning management 
systems (LMS) is not available for the classroom.

\textbf{Learn R section}

*Try R website  \url{http://tryr.codeschool.com} i dont know how to cite this with mendeley*

TryR (Code School 2014) is a web-based program but is not open source. Since public content authoring
is not available, educators are limited on what they can teach their students. The R console can be intimidating to
new statistics students so an advantage of a web-based teaching tool is
the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with
software than the statistical concepts themselves \citep{Hare2017}. When students only need their web browser to participate,
all installation complications are avoided and valuable class time can be focused on the statistics, not computer issues.

The purpose of this article is to introduce a relatively new technology, DataCamp, which incorporates the best
qualities from the teaching tools mentioned above.

DataCamp has the same reproducable capabilities as swirl but is a web-based application; educators can
create their own courses that coincide with their lessons and students can access the course without installing R.
Courses are available through the DataCamp website and students can access the lesson through their web-browser on a laptop,
tablet or moble device, making the courses accessible to anyone with an internet connection. 
The DataCamp website offers pre-existing free community courses as well as specialized \textit{Premium} classes that you need to purchase. 
However, when used for academic purposes the \textit{Premium} DataCamp content is also free for up to six months.
Any college educator can create a classroom group on the DataCamp website, add student's to the group, assign 
\textit{community} courses, \textit{Premium} courses, and even a course that they've developed themselves. 
The collection of \textit{community} courses available on DataCamp inlcude a wide range of topics from \textit{Introduction to R} to
\textit{Quantitative Risk Management in R} so novice through advanced programming students benefit.

DataCamp can be used in the classroom in a number of ways: as traditional homework assignments, as an
activity during lab periods, as pre-class assignments for a flipped classroom, and even as a test or assessment tool.

A feature that sets DataCamp apart from competing technologies is the ability to track student progress. Educators
can set deadlines for assignments and easily see not only when students complete an assignment but also which sections the
students had trouble with in a detailed report (need to cite teach page of website). Student scores can be automatically updated to a
current gradebook when you link the schools' learning management system (LMS) to DataCamp, allowing for a smooth integration of student work.

Each chapter in a DataCamp course is made up of modular exercises. Modularity is critical component in designing a statistical
learning tool because it allows independent pieces to be easily added, modified or removed from the entire functionality
\citep{Hare2017}. Course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
these exercises to meet the needs of a particular class. The only disadvantage of the modularity feature is that the sessions
are not cummulative; every exercise begins with a clear workspace so an object defined in a previous exercise needs to be
defined again.

Each of these exercises can be given a number of redeemable points which the students can see when they begin
the exercise, introducing a gamification feature to the learning experience. Students can view the exercise `hint' option and 30 percent
of the available points are deducted; all points are deducted if they ask for the solution.  If the student completes the exercise without
any help they will recieve the full points. When in a classroom group, students can view their
progress (points and chapters completed) as well as then progress of their peers. This can help students perform better
because they want to be on par with the rest of the class; furthermore, when students can see the number of available points
for an exercise it can motivate them to meet their personal achievement goals. \citep{Chang2016}.

\section{How to Use DataCamp}

\subsection{Pre-existing R courses}
In order to utilize 
DataCamp's \textit{classroom} benefits, first create an academic group on the website \url{https://www.datacamp.com/groups/education}.
After your university information has been verified and the classroom account has been approved, you can facilitate student access
by either creating a group through the DataCamp website or linking directly to your LMS.

(idk if this helps to say or is obvious) Add students by their university email address on the \textit{Members} tab and link the account to your LMS.)

\subsection{Creating a DataCamp Course}
To build a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} and
a GitHub account \url{https://github.com}. The simplest way to begin building the course is to use the template course files from the 
\texttt{Create DataCamp Course} dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
make through DataCamp will update the GitHub repository and vice versa. Every DataCamp course is linked through GitHub version control,
allowing statistics educators to easily collaborate and reproduce code. To add collaborators to the course, go to the course repository
on GitHub and under \texttt{Settings} you can enter the user names of collaborators. Collaborators who are not the primary author need 
to uncheck `My Courses' in order to view and contribute to the repository.

@@

When starting to create a DataCamp course, it is helpful to view code from pre-existing community courses which can be found on GitHub.
You can use these files as a guide to build your own course or duplicate the repository and tailor the content to fit specific needs.
The DataCamp github repository contains links to the code for several available courses; one of the most helpful when starting to build a course 
is \url{https://github.com/datacamp/courses-intro-to-r} which contains the source files for the \textit{Intoduction to R} course.

Educators are able to edit their courses in a number of ways but the \texttt{Teach Editor} located in the teach dashboard is the
most straight forward editor. The \texttt{Teach Editor} is specifically designed to make the creation process of a DataCamp course
as painless as possible, allowing writers to edit, preview, save changes and synchronize to a GitHub repository. Editing can
also be done through GitHub's online editor and through git locally but these methods do not allow for automatic content
viewing.

DataCamp courses may contain 3 different types of exercises: Normal coding exercises, Multiple choice, and Video.

A \texttt{NormalExercise} is an exercise that prompts a user to submit code. The components of this include: lesson section, instructions, pre-exercise code, sample code, hint, solution and a submission correctness testing code (SCT). (add reference to teach editor code) However, the interface for students (or the \texttt{Preview}
mode) only includes the lesson, instructions, R script panel and a R console panel (Figure~\ref{fig:code1}).

\begin{figure}
\caption{Teach Editor Interface}
\begin{verbatim}
--- type:NormalExercise lang:r xp:100 skills:1 key:9a4fea2da
## Visualizing quantitative data in R

@@

*** =instructions
- Create a histogram of the `wage` variable from the 
`CPS85` data set.
*** =hint
Follow the format from the lesson: `hist(dataset$variable)`
with specified data set and variable.
*** =pre_exercise_code
```{r}
library(mosaicData)
```
*** =sample_code
```{r}
# Create histogram of the wage variable
```
*** =solution
```{r}
# Create histogram of the wage variable 
hist(CPS85$wage)
```
*** =sct
```{r}
test_function("hist", args = "x", incorrect_msg = 
"Make sure you specify the `CPS85` data set
and `wage` variable.")
```

\end{verbatim}
\label{fig:code1}
\end{figure}

\begin{figure}[h]
  \includegraphics[scale = 0.19] {preview.jpg}
\end{figure}

@@

The submission correctness testing code (or SCT) automatically assesses if the correct code was submitted. If a student submits an 
incorrect answer, they will receive immediate feedback on what they are doing wrong and the system will guide them to the right answer.
Instructors can use the default feedback that DataCamp automatically generates or write their own custom messages. For example, figure blank
contains the default feedback for a few possible incorrect submissions of the \texttt{hist()} function.

\begin{figure}
\caption{Examples of DataCamps Default Feedback}
\begin{Verbatim}[frame=single]

Student types:
histogram(dataset$var_name)

@@

\end{Verbatim}
\label{fig:code1}
\end{figure}

The default feedback is meaningful and specific; most of the time custom 
messages are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. 
DataCamp provides a helpful R package called \textit{testwhat} which acts as a guide to writing and using SCTs (this can be accessed on DataCamp's GitHub 
repository: \url{https://github.com/datacamp/testwhat/wiki}. 
\textit{testwhat} contains functions that can test different types of problems including loops, object definitions, printed output, functions, ect.
The submission correctness testing code compares the ideal answer (from the solution) to the students answer. Different
arguements can be added to the test functions to alter the testing process and automatic feedback. (**do I cite datacamp website here?**)

%add an example of a test_function sct.... maybe plot

@@

msg_bad <- "That is not correct"
msg_success <- "Exactly! R can do all of these things."
test_mc(correct = 4, 
    feedback_msgs = c(msg_bad, msg_bad, msg_bad, msg_success))
```
\end{Verbatim}
\end{figure}

%add example of regular multiple choice exercise --> use Quick check 2 from lab 8

Video exercises act as in instructional video addition to a DataCamp course; instructors can add short videos of them explaining concepts and with 
relevent slides that appear in the background. The DataCamp website \url{https://www.datacamp.com/teach/documentation#tab_code_exercises} provides 
more detail on the content of the various exercises.

Tips for smoother course development process:
    + Using LaTeX math symbols to display greek letters, operators, ect.
    + When using datacamp and github, press 'refresh' when available on the screen

All DataCamp courses will have a course badge and most will use data sets and R packages. Information on how to add data sets and images
can be found in DataCamps 'Teach' documentation \url{https://www.datacamp.com/teach/documentation} under the 'Upload Assets' tab. However,
there is currently no information on DataCamp about integrating R packages. To use R packages in a course, you will need to create a new file
in the GitHub course repository named \texttt{requirements.r}. The file should contain: \texttt{devtools::install\_version}, package name and version for 
every package you use in the DataCamp course. For example, following code will add the \texttt{ggplot2} and \texttt{mosaic} packages to the repository.

@@

LaTeX is compatable with DataCamp course builders can use LaTeX math symbols to display Greek letters, formulas, ect. For example:
\begin{verbatim}
$H_0$: $p = 0.07$
$H_a$: $p \neq 0.07$
\end{verbatim}

@@

%Check this out, Schubert said this \cite{Schubert13}.

%Check this out, Campbell said this \cite{Campbell02} regularly, but cite this in parentheses \citep{Campbell02}.

%Check this out, Chi said this \cite{Chi81}.

%Use this for final submission
%\bibliographystyle{ECA_jasa}
\bibliographystyle{plainnat}
\bibliography{library}

>>>>

%-----------------------------------------------------------------------------------------------------
%Substitute this all with tise_style
\documentclass[12pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage{natbib}  % used for citations
\usepackage[parfill]{parskip} %used for formatting style of text
\usepackage{url}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{fancyvrb}
% Sets margins to 1 in
%\addtolength{\oddsidemargin}{-.5in}%
%\addtolength{\evensidemargin}{-.5in}%
%\addtolength{\textwidth}{1in}%
%\addtolength{\textheight}{1.3in}%
%\addtolength{\topmargin}{-.8in}%
%-----------------------------------------------------------------------------------------------------

\title{DataCamp: An Interactive Teaching Tool}

\author{Tessa Mcdonnel, Shannon Pileggi \\Statistics Department \\ California Polytechnic State University, San Luis Obispo}

\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

It is no suprise that technology plays a vital role in the field of statistics. As the technological revolution continues to
unfold, the use of statistical software has become increasingly emphasized in education \citep{AmericanStatisticalAssociation2016}. By integrating the
capabilities of technology in statistics courses, students can explore fundamental concepts by analyzing and
interpreting real data sets \citep{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is practiced outside of the
classroom \citep{Wang2017}.

The goal for any statistics course is to help students develop the ability to think statistically
\citep{AmericanStatisticalAssociation2016} and introducing technology into the curriculum can greatly strengthen this ability by illustrating concepts such as
variability, randomness and hypothesis testing. Although numerous statistical technologies exist, R and R Studio
provide extensive computational abilities (free of charge) and are commonly used in statistics courses. R
allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark
an interest in the domain of statistics \citep{Wang2017}.

\subsection{Interactive tools to learn R}
With this increased use of R in classrooms, an effective tool to familiarlize students with statistical software is needed
\citep{Baumer2014}. While R software provides users with extraordinary statistical capabilities, there is certainly a steep learning curve. To facilitate
this transition to R programming, popular interactive teaching technologies have been created including \textit{swirl} \citep{Kross} and Try R \citep{TryR}. 
These tools allow students to work through coding problems while receiving immediate feedback and can be used in and out of the classroom.

\subsubsection{\textit{swirl}}
\textit{swirl} is an
open source R package that allows students to learn R programing in the R console. This interactive learning tool
contains several pre-existing lessons and educators can also create their own
lesson to fit the specific curriculum \citep{Carchedi2014}.
While \textit{swirl} can be linked to a Massive Open Online Courses (MOOCs) like Coursera, integration of learning management 
systems (LMS) is not available for the classroom.

\subsubsection{Try R}
Try R \citep{TryR} also an interactive R programming course but unlike \textit{swirl}, Try R is web-based. 
The R console can be intimidating to
new statistics students so an advantage of a web-based teaching tool is
the clean and easy to use interface. This is an important quality given that students often struggle more with the
software used than the statistical concepts themselves \citep{Hare2017}. When students only need their web browser to participate,
all installation complications are avoided and valuable class time can be focused on the lesson.
However, Try R is not open source so public content authoring
is not available; educators are limited to the existing lessons available on the Try R website.

\section{DataCamp}

\subsection{DataCamp course features}

The purpose of this article is to introduce a new interactive teaching technology, DataCamp.

\subsubsection{DataCamp compared to similar technologies}
DataCamp provides the same reproducable capabilities as \textit{swirl} but is a web-based application. Educators can
create their own courses that coincide with specific lessons and students can access the course without installing any software.
Courses are available through the DataCamp website and students can access the lesson through their web-browser on a laptop,
tablet or moble device, making the courses accessible to anyone with an internet connection. The programming courses can be used in the 
classroom in a number of ways: as traditional homework assignments, as an activity during lab periods, as pre-class assignments
for a flipped classroom, and even as a test or assessment tool.

\subsubsection{Wide variety of course topics}
The DataCamp website offers pre-existing free community courses as well as more specialized \textit{Premium} classes that require a fee. 
The collection of \textit{community} courses available on DataCamp inlcude a wide range of topics from \textit{Introduction to R} to
\textit{Quantitative Risk Management in R} so novice through advanced programming students benefit.

\subsubsection{Integration with Learning Management Systems}
One feature that sets DataCamp apart from competing technologies is the ability to track student progress. Educators
can set deadlines for assignments and view which sections the
students had trouble with in a detailed report. DataCamp courses can also be linked to the school's learning management system (LMS) so student scores are automatically updated to the
current gradebook, allowing for a smooth integration of student work.

\subsubsection{Modularity}
DataCamp courses are broken up into chapters and each chapter is composed of modular exercises. Modularity is a critical component in designing a
learning tool because it allows independent pieces to be easily added, modified or removed from the entire functionality
\citep{Hare2017}. DataCamp course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
these exercises to meet the needs of a particular class. The only disadvantage of the modularity feature is that the sessions
are not cummulative; every exercise begins with a clear workspace so an object defined in a previous exercise needs to be
defined again.

\subsubsection{Gamification}
Each chapter exercise is given a specified number of redeemable points which the students can see when they begin
the exercise, introducing a gamification feature to the learning experience. When in a classroom group, students can view their
progress (points and chapters completed) as well as then progress of their peers. This can help students perform better
because they want to be on par with the rest of the class; furthermore, when students can see the number of available points
for an exercise it can motivate them to meet their personal achievement goals. \citep{Chang2016}. If the student completes the exercise without
any assistance, they will recieve the full points. If the student is having trouble with a problem, they can view the exercise `hint' option and 30 percent
of the available points are deducted; all points are deducted if they ask for the solution. 
\subsection{Pre-existing R courses}
In order to utilize 
DataCamp's \textit{classroom} benefits, first create an academic group on the website \url{https://www.datacamp.com/groups/education}.
After your university information has been verified and the classroom account has been approved, access is facilitated 
by either creating a group through the DataCamp website or linking directly to your LMS. You can add students to the course by their university email address on the \textit{Members} tab.
\section{Creating a DataCamp Course}
\subsection{Getting Started}
To build a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} as well as
a GitHub account \url{https://github.com}. Every DataCamp course is linked through GitHub version control,
allowing statistics educators to easily collaborate and reproduce code. To add collaborators to the course, go to the course repository
on GitHub and under \texttt{Settings} you can enter the user names of collaborators. Collaborators who are not the primary author need 
to uncheck `My Courses' in order to view and contribute to the repository. The simplest way to begin building the course is to use the template course files from the
\texttt{Create DataCamp Course} dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
made through DataCamp will update the GitHub repository and vice versa.

@@

\subsection{Course Editing}
Educators are able to edit their courses in a number of ways but the \texttt{Teach Editor} located in the teach dashboard is the
most straight forward editor. The \texttt{Teach Editor} is specifically designed to make the creation process of a DataCamp course
as painless as possible, allowing writers to edit, preview, save changes and synchronize to a GitHub repository. Editing can
also be done through GitHub's online editor or through git locally but these methods do not allow for automatic content
viewing.
\subsection{Components of a DataCamp Course}
\subsubsection{Exercise Layout}
Figure1 is an example of an interactive coding exercise for an introductory statistics course. Students will read the lesson information and instructions, answer the question, and submit their code; it should take approximately 5 minutes to complete this exercise.
\begin{figure}
\caption{Teach Editor Interface}
\begin{Verbatim}[frame=single]
--- type:NormalExercise lang:r xp:100 skills:1 key:9a4fea2da
## Visualizing quantitative data in R

@@

*** =instructions
- Create a histogram of the `wage` variable from the 
`CPS85` data set.
*** =hint
Follow the format from the lesson: `hist(dataset$variable)`
with specified data set and variable.
*** =pre_exercise_code
```{r}
library(mosaicData)
```
*** =sample_code
```{r}
# Create histogram of the wage variable
```
*** =solution
```{r}
# Create histogram of the wage variable 
hist(CPS85$wage)
```
*** =sct
```{r}
test_function("hist", args = "x", incorrect_msg = 
"Make sure you specify the `CPS85` data set
and `wage` variable.")
```
\end{Verbatim}
\label{fig:code1}
\end{figure}

\begin{figure}[h]
  \includegraphics[scale = 0.40] {preview.jpg}
\end{figure}

@@

\subsubsection{Submission Correctness Test}
The submission correctness testing code (or SCT) automatically assesses if the correct code was submitted. If a student submits an 
incorrect answer, they will receive immediate feedback on what they are doing wrong and the system will guide them to the right answer.
Instructors can use the default feedback that DataCamp automatically generates or write their own custom messages. For example, figure blank
contains the default feedback for a few possible incorrect submissions of the \texttt{hist()} function.

\begin{figure}
\caption{Examples of DataCamps Default Feedback}
\begin{Verbatim}[frame=single]
Student types:
histogram(dataset$var_name)

@@

\end{Verbatim}
\label{fig:code1}
\end{figure}
The default feedback is meaningful and specific; most of the time custom 
messages are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. 
DataCamp provides a helpful R package called \textit{testwhat} which acts as a guide to writing and using SCTs (this can be accessed on DataCamp's GitHub 
repository: \url{https://github.com/datacamp/testwhat/wiki}. 
\textit{testwhat} contains functions that can test different types of problems including loops, object definitions, printed output, functions, ect.
The submission correctness testing code compares the ideal answer (from the solution) to the students answer. Different
arguements can be added to the test functions to alter the testing process and automatic feedback. (**do I cite datacamp website here?**)

\subsection{DataCamp Exercise Types}
DataCamp courses may contain 3 different types of exercises: Normal coding, video, and multiple choice exercises.
\subsubsection{Normal Exercise}
A \texttt{NormalExercise} is an exercise that prompts a user to submit code. The components of this include: lesson section, instructions, pre-exercise code, sample code, hint, solution and a submission correctness testing code (SCT). (add reference to teach editor code) However, the interface for students (or the \texttt{Preview}
mode) only includes the lesson, instructions, R script panel and a R console panel (Figure~\ref{fig:code1}).
\subsubsection{Video Exercise}
Video exercises act as in instructional video addition to a DataCamp course; instructors can add short videos of them explaining concepts and with 
relevent slides that appear in the background. The DataCamp website \url{https://www.datacamp.com/teach/documentation#tab_code_exercises} provides 
more detail on the content of the various exercises.

\subsubsection{Multiple Choice Exercise}

@@

msg_bad <- "That is not correct"
msg_success <- "Exactly! R can do all of these things."
test_mc(correct = 4, 
    feedback_msgs = c(msg_bad, msg_bad, msg_bad, msg_success))
```
\end{Verbatim}
\end{figure}
\subsection{Advise for smoother course development}
DataCamp is fairly new so the only existing information on creating a course is on the DataCamp website. While writing my first introductory R programming class on DataCamp, I learned a few tricks that I wish I knew before I started. 
\subsubsection{GitHub repositories}
When creating your first DataCamp course, it is helpful to view code from pre-existing community courses which can be found on GitHub.
DataCamp's github repository contains links to the code for several available courses; one of the most helpful when starting to build a course 
is \url{https://github.com/datacamp/courses-intro-to-r} which contains the source files for the \textit{Intoduction to R} course.
You can use these files as a guide to build your own course or duplicate the repository and tailor the content to fit specific needs.

\subsubsection{Integrating R packages}
All DataCamp courses will have a course badge and most will use data sets and R packages. Information on how to add data sets and images
can be found in DataCamps 'Teach' documentation \url{https://www.datacamp.com/teach/documentation} under the 'Upload Assets' tab. However,
there is currently no information on DataCamp about integrating R packages. To use R packages in a course, you will need to create a new file
in the GitHub course repository named \texttt{requirements.r}. The file should contain: \texttt{devtools::install\_version}, package name and version for 
every package you use in the DataCamp course. For example, following code will add the \texttt{ggplot2} and \texttt{mosaic} packages to the repository.

@@

\subsubsection{TeX typesetting}
LaTeX is compatable with DataCamp course builders can use LaTeX math symbols to display Greek letters, formulas, ect. For example:
\begin{verbatim}
$H_0$: $p = 0.07$
$H_a$: $p \neq 0.07$
\end{verbatim}

@@

\section{Conclusion}

\bibliographystyle{plainnat}
\bibliography{library}
